On the Gravitational stability of gravito-turbulent accretion disks

### 2016-02-02 paper/application.tex
to be submitted version done

%KMK
%However, $\theta$ is no longer a direct proxy for the irradiation level
%as it was in the standard beta cooling model.
%is now an effective irradiation level. 
Eq. \ref{real_theta} shows that the re-defined $\theta$ is related to
the true irradiation temperature $\tirr$ through the function $g$ given by 
Eq. \ref{g_def}, and is therefore a only a weak function of the irradiation temperature. 
%A physically non-irradiated disk with $\tirr=0$ will 
%have a non-zero value of the `irradiation parameter', $\theta\neq0$. 
More specifically $\theta = O(1)$ 
for all $\tirr <T$, and for our adopted opacity law, Eq. \ref{opacity_law}, 
\begin{align*}
  \theta = \frac{4-g}{4-2g}. 
\end{align*}
Thus for $T_\mathrm{irr} = 0$ we have $5/6<\theta<3/2$ by considering
$\tau\to 0,\,\infty$. However, for $T=\tirr$ we have $\theta = 1$, as
expected intuitively.    
%%KMK 
%This results from the fact that PPD cooling generally depends on both
%$P$ and $\Sigma$, but in the absence of irradiation standard beta
%cooling only depends on $P$. 
%{\bf KMK: we should discuss}

@@

The fiducial disk is subject to viscous GI on dynamical timescales
($\lesssim 10$ orbits) for $R\gtrsim60$AU. We note this transition
radius is also implied by Eq. 16 in \cite{kratter10}. Coincidentally,
beyond this radius $\alpha\gtrsim 0.1$ (and 
$\beta\lesssim 3$), which is often quoted as a condition for disk
fragmentation   
\citepalias[e.g.][]{rafikov15}. Thus viscous GI may be responsible for 
the transition between gravito-turbulence and fragmentation due to the
removal of rotational support by viscous (turbulent) stresses.

>>>>

%KMK
%However, $\theta$ is no longer a direct proxy for the irradiation level
%as it was in the standard beta cooling model.
%is now an effective irradiation level. 
Eq. \ref{real_theta} shows that $\theta$ 
is related to the true irradiation temperature $\tirr$ through the function $g$ given by 
Eq. \ref{g_def}, and is therefore a only a weak function of the irradiation temperature. 
%A physically non-irradiated disk with $\tirr=0$ will 
%have a non-zero value of the `irradiation parameter', $\theta\neq0$. 
More specifically $\theta = O(1)$ 
for all $\tirr <T$, and for our adopted opacity law, Eq. \ref{opacity_law}, 
\begin{align*}
  \theta = \frac{4-g}{4-2g}. 
\end{align*}
Thus for $T_\mathrm{irr} = 0$ we have $5/6<\theta<3/2$ by considering
$\tau\to 0,\,\infty$. However, for $T=\tirr$ we have $\theta = 1$, as
expected intuitively.    
%%KMK 
%This results from the fact that PPD cooling generally depends on both
%$P$ and $\Sigma$, but in the absence of irradiation standard beta
%cooling only depends on $P$. 
%{\bf KMK: we should discuss}

@@

The fiducial disk is subject to viscous GI on dynamical timescales
($\lesssim 10$ orbits) for $R\gtrsim60$AU. We note this transition
radius is also implied by Eq. 16 in \cite{kratter10}. Coincidentally,
beyond this radius $\alpha\gtrsim 0.1$ (and 
$\tcool\Omega\lesssim 3$), which is often quoted as a condition for disk
fragmentation   
\citepalias[e.g.][]{rafikov15}. Thus viscous GI may be responsible for 
the transition between gravito-turbulence and fragmentation due to the
removal of rotational support by viscous (turbulent) stresses.

### 2016-02-02 paper/summary.tex
to be submitted version done

We apply our linear framework to protoplanetary disks with 
realistic models for cooling and gravito-turbulence. 
We show that with a physically motivated cooling model for PPDs, 
cooling alone does not lead to gravitational instabilities. This is
due to stabilization by an effective `irradiation' associated with the
PPD cooling function, which is present even if there is no physical
irradiation. 
This effective irradiation arises because, for the stability problem,
%cf eqm disk 
a non-zero floor temperature is generally required in the cooling
prescription (Eq. \ref{beta_cool}) in order to map it to PPD cooling,
regardless of the actual irradiation temperature.

>>>>

We apply our linear framework to protoplanetary disks with 
realistic models for cooling and gravito-turbulence. 
We show that with a physically motivated cooling model for PPDs, 
cooling alone does not lead to gravitational instabilities. This is
due to stabilization by an effective `irradiation' associated with the 
density-dependence of the PPD cooling function as it appears in the
stability problem, which is present even if there is no physical
irradiation.  
%This effective irradiation arises because, for the stability problem,
%cf eqm disk 
%a non-zero floor temperature is generally required in the cooling
%prescription (Eq. \ref{beta_cool}) in order to map it to PPD cooling,
%regardless of the actual irradiation temperature.
